BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-28 tex/0-abstract.tex
Add sublime project.
Progress...

Blogs are by nature a very dynamic and volatile communication medium. The
BlogForever project aims to provide a generic platform for blog preservation,
thus ensuring access to this information to future generations. This paper
presents a key component of this archiving system: the web crawler. More
precisely, our discussion will concentrate on techniques to automatically
extract content, authors, date and comments of blog posts. One of the main
challenges in the preservation of web objects is the rapid evolution of
technologies. For instance, the recent trend towards using JavaScript to
dynamically generate pages on the client side constitutes a new obstacle for
today's crawlers. We will show how we integrated a headless web browser into the
harvesting process in order to address these matters. Furthermore, we present a
simple and robust algorithm based on string matching between web feeds and page
content to generate wrappers. Being applicable to all posts of a blog, the
resulting extraction procedure scales for large blogs.

>>>>

Blogs are by nature a very dynamic and volatile communication medium. The BlogForever project aims on providing a generic platform for blog preservation, thus ensuring access to this information for future generations. This paper presents a key component of this archiving system: the web crawler. More precisely, our discussion will concentrate on techniques to automatically extract content, authors, dates and comments from blog posts. One of the main challenges in the preservation of web objects is the rapid evolution of technologies. For instance, the recent trend towards using JavaScript to dynamically generate pages on the client side constitutes a new obstacle for today's crawlers. We will show how we integrated a web browser into the harvesting process in order to address this issue. Furthermore, we will present a simple and robust algorithm based on string matching between web feeds and page content to generate wrappers. Being applicable to all posts of a blog, the resulting extraction process scales to blogs with large amounts of posts.
\comment{"being applicable to all posts of a blog" --> sounds a bit weird.}

### 2013-11-28 tex/3-algorithms.tex

The Sørensen–Dice coefficient methods operate by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:

>>>>

The Sørensen–Dice coefficient method operates by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:
